---
title: "Sampling Contamination 3D"
author: "Xianbin Cheng"
date: "January 29, 2019"
output: html_document
---

# Method #

1. Load in libraries, visualization functions and check the session info.

```{r, warning = FALSE, message= FALSE}
source(file = "Sampling_libraries.R")
source(file = "Sampling_contamination.R")
source(file = "Sampling_visualization.R")
library(plotly)
```

2. Define the input paramaters and create a simulation function.

* `n_contam` = the number of contamination points  
* `x_lim` = the limits of the x-axis  
* `y_lim` = the limits of the y-axis  
* `z_lim` = the limits of the z-axis
* `x` = the horizontal coordinate of the contamination center, which follows a uniform distribution by default
* `y` = the vertical coordinate of the contamination center, which follows a uniform distribution by default
* `z` = the vertical coordinate of the contamination center, which follows a uniform distribution by default
* `cont_level` = a vector that indicates the mean contamination level (logCFU/g or logCFU/mL) and the standard deviation in a log scale, assuming contamination level follows a log normal distribution $ln(cont\_level)$~$N(\mu, \sigma^2)$. 

**Discrete Spread**

* `n_affected` = the number of affected kernels near the contamination spot, which follows a Poisson distribution ($Pois(\lambda = 5)$)   
* `covar_mat` = covariance matrix of `x` and `y`, which defines the spread of contamination. Assume the spread follows a 2D normal distribution with var(X) = 0.25, var(Y) = 0.25 and cov(X, Y) = 0  


```{r}
## The input parameters
n_contam = rpois(n = 1, lambda = 3)
x_lim = c(0, 10)
y_lim = c(0, 10)
z_lim = c(0, 10)
lims = list(xlim = x_lim, ylim = y_lim, zlim = z_lim)
cont_level = c(7, 1)

### Mode 1
n_affected = rpois(n = 1, lambda = 5)
covar_mat = matrix(data = c(0.25, 0, 0, 0, 0.25, 0, 0, 0, 0.25), nrow = 3, ncol = 3)

```

3. Generate contamination.

```{r}
unif_contam = function(n_contam, lims){
  x = runif(n = n_contam, min = lims$xlim[1], max = lims$xlim[2])
  y = runif(n = n_contam, min = lims$ylim[1], max = lims$ylim[2])
  z = runif(n = n_contam, min = lims$zlim[1], max = lims$zlim[2])
  
  data.frame(x = x, y = y, z = z)
}

spot_coord = unif_contam(n_contam = n_contam, lims = lims)




```


# Result

```{r}
scatter3D(x = test$V1, y = test$V2, z = test$V3, type = "p", col = "black", 
          xlim = c(0, 10), ylim = c(0, 10), zlim = c(0, 10), phi = 20, theta = 40 )

```

