---
title: 'Sampling: Analysis 3'
author: "Xianbin Cheng"
date: "January 9, 2019"
output: html_document
---

# Objective  

  * To analyze the simulated data (low prevalence) using linear regression.
  
# Methods

1. Load the libraries and functions.

```{r, warning = FALSE, message = FALSE}
source("Sampling_libraries.R")
source("Sampling_contamination.R")
source("Sampling_plan.R")
source("Sampling_assay.R")
source("Sampling_outcome.R")
source("Sampling_iteration.R")
source("Sampling_analysis.R")
source("Simulation_data.R")
source("Sampling_visualization.R")
source("Sampling_assay_prep.R")
library(lawstat)
```

```{r}
sessionInfo()
```


2. List important parameters from previous R files. 

**Contamination:**  

  * `n_contam` = the number of contamination points 
  * `x_lim` = the limits of the horizontal axis  
  * `y_lim` = the limits of the vertical axis  
  * `x` = the horizontal coordinate of the contamination center, which follows a uniform distribution (`U(0,10)`)
  * `y` = the vertical coordinate of the contamination center, which follows a uniform distribution(`U(0,10)`)  
  * `cont_level` = a vector that indicates the mean contamination level (logCFU/g or logCFU/mL) and the standard deviation in a log scale, assuming contamination level follows a log normal distribution $ln(cont\_level)$~$N(\mu, \sigma^2)$. 
  * `spread` = the type of spread: `continuous` or `discrete`.

  **Mode 1: Discrete Spread** 

  * `n_affected` = the number of affected plants near the contamination spot, which follows a Poisson distribution (`Pois(lambda = 5)`)   
  * `covar_mat` = covariance matrix of `x` and `y`, which defines the spread of contamination. Assume the spread follows a 2D normal distribution with var(X) =     0.25, var(Y) = 0.25 and cov(X, Y) = 0  

  **Mode 2: Continuous Spread**

  * `spread_radius` = the radius of the contamination spread. 
  * `LOC` = the limit of contribution of contamination. By default, it is set at 0.001.(Both `spread_radius` and `LOC` determine the shape of decay function that describes how much contamination from the source is contributed to a target point.)
  * `fun` = the decay function that describes the spread. It takes either "exp" or "norm".

**Sampling Plan:**  

  * `method_sp` = the sampling method (SRS, STRS, SS)
  * `n_sp` = the number of sampling points
  * `sp_radius` = the radius (m) of a circular region around the sample point. (Only applicable to **Mode 1: Discrete Spread**)
  * `n_strata` = the number of strata (applicable to *Stratified random sampling*)
  * `by` = the side along which the field is divided into strata. It is either "row" or "column" (applicable to *Stratified random sampling*) **OR** the side along which a sample is taken every k steps (applicable to *Systematic sampling*).
  * `m_kbar` = averaged kernel weight (g). By default, it's 0.3 g (estimated from Texas corn).
  * `m_sp` = the analytical sample weight (25 g)
  * `conc_good` = concentration of toxin in healthy kernels
  * `case` = 1 ~ 15 cases that define the stringency of the sampling plan.
  * Attributes plans:
      + `n` = number of analytical units (25g)
      + `c` = maximum allowable number of analytical units yielding positive results
      + `m` = microbial count or concentration above which an analytical unit is considered positive
      + `M` = microbial count or concentration, if any analytical unit is above `M`, the lot is rejected.

**Sampling Assay:**
  
  * `method_det` = method of detection
      + Plating: LOD = 2500 CFU/g
      + Enrichment: LOD = 1 CFU/g

**Iteration:**

  * `n_iter` = the number of iterations per simulation.

```{r}
## We choose "n_contam" to iterate on.
n_contam = 10

## Other fixed parameters
## Contamination
x_lim = c(0, 100)
y_lim = c(0, 100)
cont_level = c(4, 1)
spread = "continuous"

### Mode 1
n_affected = rpois(n = 1, lambda = 5)
covar_mat = matrix(data = c(0.25, 0, 0, 0.25), nrow = 2, ncol = 2)

### Mode 2
spread_radius = 2.5
LOC = 10^(-3)
fun = "exp"

## Sampling plan
method_sp = "srs"
n_sp = 15
sp_radius = 1
n_strata = 5
by = "row"
m_kbar = 0.3
m_sp = 25
conc_good = 0.1
case = 12
m = 0
M = 0
Mc = 20

## Assay
method_det = "enrichment"

## Sampling outcome
n_iter = 100
```

3. Show the different combinations of `n_contam`, `n_sp`, `method_sp` to be analyzed.

```{r}
# First layer
param_name = "n_contam"
vals = c(1,4,8,16,40,80)

# Second layer
strategy_list = c("srs", "strs", "ss")

# Third layer
n_sp_list = c(5, 10, 15, 20, 30, 60)
case_list = c(10, 11, 13, 12, 14, 15) # According to the attribute plan
```

```{r, echo = FALSE}
temp = data.frame(n_contam = "1,4,8,16,40,80",
                  prevalence = "0.1%,0.5%,1%,2%,5%,10%",
                  n_sp = n_sp_list,
                  n_strata = n_strata,
                  by = by,
                  spread = spread,
                  method_sp = "srs/strs/ss",
                  case = case_list,
                  c = 0, 
                  m = m, 
                  iteration = n_iter*n_iter)

kable_styling(kable(temp, format = "html", 
                    caption = "TABLE. Combinations of input parameters"),
              full_width = FALSE)
```

4. Read the simulation data.

```{r}
full_data = read.csv(file = "sim_data_1to80_5to60_3_10to15.csv", header = TRUE, stringsAsFactors = FALSE)
```

5. Build a linear regression model on the simulation data.

  * Model: $Y = \beta_0 + \beta_1X_1+\beta_2X_2+ \beta_3X_3 + \beta_4X_1X_2+\beta_5X_1X_3+\beta_6X_2X_3+\varepsilon$
  
  * Main effects: `n_contam`, `method_sp`, `n_sp`. `method_sp` is a categorical variable with three levels: `srs`, `strs`, `ss`.
  
  * Interaction effects: two-way interactions of the above parameters

```{r}
model = lm(formula = P_det ~ param + method_sp + n_sp + param:method_sp + param:n_sp + method_sp:n_sp, data = full_data)
```

6. Run the simulation once for visualization purpose.

```{r}
ArgList = list(n_contam = n_contam, xlim = x_lim, ylim = y_lim, n_affected = n_affected, covar_mat = covar_mat, spread_radius = spread_radius, method_sp = method_sp, n_sp = n_sp, sp_radius = sp_radius, spread = spread, n_strata = n_strata, by = by, cont_level = cont_level, LOC = LOC, fun = fun, m_kbar = m_kbar, m_sp = m_sp, conc_good = conc_good, case = case, m = m, M = M, Mc = Mc, method_det = method_det)

one_iteration = do.call(what = sim_outcome_temp, args = ArgList) %>% .[[4]]

# SRS
ArgList_srs = list(n_contam = n_contam, xlim = x_lim, ylim = y_lim, n_affected = n_affected, covar_mat = covar_mat, spread_radius = spread_radius, method_sp = "srs", n_sp = n_sp, sp_radius = sp_radius, spread = spread, n_strata = n_strata, by = by, cont_level = cont_level, LOC = LOC, fun = fun, m_kbar = m_kbar, m_sp = m_sp, conc_good = conc_good, case = case, m = m, M = M, Mc = Mc, method_det = method_det)

one_iteration_srs = do.call(what = sim_outcome_temp, args = ArgList_srs) %>% .[[4]]

# STRS
ArgList_strs = list(n_contam = n_contam, xlim = x_lim, ylim = y_lim, n_affected = n_affected, covar_mat = covar_mat, spread_radius = spread_radius, method_sp = "strs", n_sp = n_sp, sp_radius = sp_radius, spread = spread, n_strata = n_strata, by = by, cont_level = cont_level, LOC = LOC, fun = fun, m_kbar = m_kbar, m_sp = m_sp, conc_good = conc_good, case = case, m = m, M = M, Mc = Mc, method_det = method_det)

one_iteration_strs = do.call(what = sim_outcome_temp, args = ArgList_strs) %>% .[[4]]

# SS
ArgList_ss = list(n_contam = n_contam, xlim = x_lim, ylim = y_lim, n_affected = n_affected, covar_mat = covar_mat, spread_radius = spread_radius, method_sp = "ss", n_sp = n_sp, sp_radius = sp_radius, spread = spread, n_strata = n_strata, by = by, cont_level = cont_level, LOC = LOC, fun = fun, m_kbar = m_kbar, m_sp = m_sp, conc_good = conc_good, case = case, m = m, M = M, Mc = Mc, method_det = method_det)

one_iteration_ss = do.call(what = sim_outcome_temp, args = ArgList_ss) %>% .[[4]]
```

#Result

1. Visualization

```{r, warning = FALSE, echo = FALSE, out.width = "33%"}
overlay_draw(method_sp = method_sp, data = one_iteration, spread = spread, xlim = x_lim, ylim = y_lim, n_strata = n_strata, by = by)
contam_level_draw(dimension = "3d", method = fun, spread_radius = spread_radius, LOC = LOC, df_contam = one_iteration, xlim = x_lim, ylim = y_lim)
assay_draw(df = one_iteration, M = M, m = m, Mc = Mc, method_det = method_det, spread = spread, case = case)
```

2. Linear regression results

```{r}
summary(model)
plot(model)
```

3. Comparison among three sampling strategies across different prevalence levels or different sample sizes.

```{r}
p_contam = ggplot(data = full_data, aes(x = param, y = P_det, group = interaction(param, method_sp))) +
    geom_boxplot(aes(color = method_sp)) +
    scale_x_log10(breaks = full_data$param) +
    scale_color_discrete(name = "Sampling strategy", labels = c("SRS", "SS", "STRS")) +
    coord_cartesian(ylim = c(0,1)) +
    labs(x = "Number of contamination points", y = "Probability of detection") +
    theme_bw() +
    theme(legend.position = "top")
```

```{r}
p_sp = ggplot(data = full_data, aes(x = n_sp, y = P_det, group = interaction(n_sp, method_sp))) +
    geom_boxplot(aes(color = method_sp)) +
    scale_x_log10(breaks = full_data$n_sp) +
    coord_cartesian(ylim = c(0,1)) +
    scale_color_discrete(name = "Sampling strategy", labels = c("SRS", "SS", "STRS")) +
    labs(x = "Number of samples", y = "Probability of detection") +
    theme_bw() +
    theme(legend.position = "top")
```

```{r}
p_srs = overlay_draw(method_sp = "srs", data = one_iteration_srs, spread = spread, xlim = x_lim, ylim = y_lim, n_strata = n_strata, by = by)
p_strs = overlay_draw(method_sp = "strs", data = one_iteration_strs, spread = spread, xlim = x_lim, ylim = y_lim, n_strata = n_strata, by = by)
p_ss = overlay_draw(method_sp = "ss", data = one_iteration_ss, spread = spread, xlim = x_lim, ylim = y_lim, n_strata = n_strata, by = by)

pdf(file = "CPS_Poster.pdf")
  p_srs
  p_strs
  p_ss
  p_contam
  p_sp
dev.off()
```


4. Run ANOVA to compare the mean probability of detection for three sampling strategies.

```{r}
# Different prevalence levels
f_anova = function(val){
  mod = aov(formula = P_det ~ as.factor(method_sp), data = subset(x = full_data, subset = param == val))
  summary(mod)
}

map(.x = vals, .f = f_anova)

# Different sample sizes
f_anova2 = function(val){
  mod = aov(formula = P_det ~ as.factor(method_sp), data = subset(x = full_data, subset = n_sp == val))
  summary(mod)
}

map(.x = n_sp_list, .f = f_anova2)
```

5. Compare the variances among the three sampling strategies using Brown-Forsythe Levene's test.

```{r}
f_bfl = function(val){
  levene.test(y = subset(x = full_data, subset = param == val, select = P_det, drop = TRUE), group = subset(x = full_data, subset = param == val, select = method_sp, drop = TRUE), location = "median")
}

map(.x = vals, .f = f_bfl)
```


  