---
title: "Sampling Iteration"
author: "Xianbin Cheng"
date: "September 16, 2018"
output: html_document
---

# Method

1. Source R code from `Sampling_libraries.R`, `Sampling_contamination.R`, `Sampling_plan.R`, `Sampling_assay.R` and `Sampling_outcome.R`.

```{r, warning = FALSE, message = FALSE}
source(file = "Sampling_libraries.R")
source(file = "Sampling_contamination.R")
source(file = "Sampling_plan.R")
source(file = "Sampling_outcome.R")
source(file = "Sampling_iteration.R")
source(file = "Sampling_assay.R")
```

```{r}
sessionInfo()
```

2. List important parameters from previous R files. Create a new parameter called `n_iter`.

**Contamination:**  

  * `n_contam` = the number of contamination points 
  * `x_lim` = the limits of the horizontal axis  
  * `y_lim` = the limits of the vertical axis  
  * `x` = the horizontal coordinate of the contamination center, which follows a uniform distribution (`U(0,10)`)
  * `y` = the vertical coordinate of the contamination center, which follows a uniform distribution(`U(0,10)`)  
  * `cont_level` = a vector that indicates the mean contamination level (logCFU/g or logCFU/mL) and the standard deviation in a log scale, assuming contamination level follows a log normal distribution $ln(cont\_level)$~$N(\mu, \sigma^2)$. 
  * `spread` = the type of spread: `continuous` or `discrete`.

  **Mode 1: Discrete Spread** 

  * `n_affected` = the number of affected plants near the contamination spot, which follows a Poisson distribution (`Pois(lambda = 5)`)   
  * `covar_mat` = covariance matrix of `x` and `y`, which defines the spread of contamination. Assume the spread follows a 2D normal distribution with var(X) =     0.25, var(Y) = 0.25 and cov(X, Y) = 0  

  **Mode 2: Continuous Spread**

  * `spread_radius` = the radius of the contamination spread. 
  * `LOC` = the limit of contribution of contamination. By default, it is set at 0.001.(Both `spread_radius` and `LOC` determine the shape of decay function that describes how much contamination from the source is contributed to a target point.)
  * `fun` = the decay function that describes the spread. It takes either "exp" or "norm".

**Sampling Plan:**  

  * `method_sp` = the sampling method (SRS, STRS, SS)
  * `n_sp` = the number of sampling points
  * `sp_radius` = the radius (m) of a circular region around the sample point. (Only applicable to **Mode 1: Discrete Spread**)
  * `n_strata` = the number of strata (applicable to *Stratified random sampling*)
  * `by` = the side along which the field is divided into strata. It is either "row" or "column" (applicable to *Stratified random sampling*) **OR** the side along which a sample is taken every k steps (applicable to *Systematic sampling*).
  * `m_kbar` = averaged kernel weight (g). By default, it's 0.3 g (estimated from Texas corn).
  * `m_sp` = the analytical sample weight (25 g)
  * `conc_good` = concentration of toxin in healthy kernels
  * `case` = 1 ~ 15 cases that define the stringency of the sampling plan.
  * Attributes plans:
      + `n` = number of analytical units (25g)
      + `c` = maximum allowable number of analytical units yielding positive results
      + `m` = microbial count or concentration above which an analytical unit is considered positive
      + `M` = microbial count or concentration, if any analytical unit is above `M`, the lot is rejected.

**Sampling Assay:**
  
  * `method_det` = method of detection
      + Plating: LOD = 2500 CFU/g
      + Enrichment: LOD = 1 CFU/g

**Iteration:**

  * `n_iter` = the number of iterations per simulation.

```{r}
## Contamination
n_contam = rpois(n = 1, lambda = 3)
x_lim = c(0, 10)
y_lim = c(0, 10)
cont_level = c(7, 1)
spread = "continuous"

### Mode 1
n_affected = rpois(n = 1, lambda = 5)
covar_mat = matrix(data = c(0.25, 0, 0, 0.25), nrow = 2, ncol = 2)

### Mode 2
spread_radius = 2.5
LOC = 10^(-3)
fun = "exp"

## Sampling plan
method_sp = "srs"
n_sp = 10
sp_radius = 1
n_strata = 5
by = "row"
m_kbar = 0.3
m_sp = 25
conc_good = 0.1
case = 9
m = 50
M = 500
Mc = 20

## Assay
method_det = "plating"

## Sampling outcome
n_iter = 100
```

3. Create a master function called `sim_outcome()` that takes the inputs above and iterate the simulation once.

* Intermediate data output includes `contam_xy`, `sp_xy`, `contam_sp_xy`, `dist_contam_sp`, and `cover`.
* `I_det` = A binary indicator for whether any contamination has been detected (1 = yes, 0 = no).
* `ROD` = rate of detection (how many contamination points have been detected or how many samples have captured contamination).
* `decision` = a number that represents a decision for the lot (accept or reject).

```{r}
sim_outcome
```

4. Create a function factory called `gen_sim_outcome()` that creates a child function `sim_outcome()` which has been loaded with input parameters. 

```{r}
gen_sim_outcome 

f_outcome = gen_sim_outcome(n_contam = n_contam, xlim = x_lim, ylim = y_lim, n_affected = n_affected, covar_mat = covar_mat, spread_radius = spread_radius, method = method_sp, n_sp = n_sp, sp_radius = sp_radius, spread = spread, n_strata = n_strata, by = by, cont_level = cont_level, LOC = LOC, fun = fun, m_kbar = m_kbar, m_sp = m_sp, conc_good = conc_good, case = case, m = m, M = M, Mc = Mc, method_det = method_det)
```

5. Iterate the simulation with the same input parameters. Variability exists in the coordinates of contamination points, the coordinates of sample points, and specific contamination levels. Each iteration produces three numbers: `I_det`, `ROD`, and `decision`.

```{r}
sim_iterate
calc_Pdet
calc_Prej
```

```{r}
results = sim_iterate(n_iter = n_iter, fun = f_outcome)
results2 = clean(results)
```

# Results

1. Iterate the simulation once using two different methods. With the same random number seed, they should produce the same results.

```{r}
# Run once using the bare function sim_outcome()
set.seed(123)
sim_outcome(n_contam = n_contam, xlim = x_lim, ylim = y_lim, n_affected = n_affected, covar_mat = covar_mat, spread_radius = spread_radius, method = method_sp, n_sp = n_sp, sp_radius = sp_radius, spread = spread, n_strata = n_strata, by = by, cont_level = cont_level, LOC = LOC, fun = fun, m_kbar = m_kbar, m_sp = m_sp, conc_good = conc_good, case = case, m = m, M = M, Mc = Mc, method_det = method_det)

# Run once using the child function f_outcome()
set.seed(123)
f_outcome()
```

2. Iterate the simulation for `r n_iter` times.  

    2.1. Calculate the probability of detection.  

```{r}
calc_Pdet(results2$I_det)
```


    2.2. Boxplot of the rate of detection.  

```{r}
ggplot() +
  stat_boxplot(aes(x = spread, y = results2$ROD), geom = "errorbar") +
  geom_boxplot(aes(x = spread, y = results2$ROD)) +
  geom_point(aes(x = spread, y = mean(results2$ROD)), color = "coral", shape = 4, size = 5) +
  labs(title = paste("n_contam = ", n_contam, ", n_affected <= ", n_affected,", n_sp = ", n_sp, ", n_iter = ", n_iter , sep = ""), 
       x = NULL,
       y = "ROD") +
  coord_fixed(ratio = 1, ylim = c(0,1)) +
  theme_bw()
```

    2.3. Calculate the probability of acceptance.

```{r}
1 - calc_Prej(results2$decision)
```

