---
title: 'Sampling: Sampling Plan'
author: "Xianbin Cheng"
date: "September 7, 2018"
output: html_document
---

# Method

1. Load libraries and source R code.

```{r, warning = FALSE, message = FALSE}
source(file = "Sampling_libraries.R")
source(file = "Sampling_contamination.R")
source(file = "Sampling_visualization.R")
source(file = "Sampling_plan.R")
```

```{r}
sessionInfo()
```

2. List important parameters from `Sampling_contamination.R`.

* `n_contam` = the number of contamination points  
* `x_lim` = the limits of the horizontal axis  
* `y_lim` = the limits of the vertical axis  
* `x` = the horizontal coordinate of the contamination center, which follows a uniform distribution (`U(0,10)`)
* `y` = the vertical coordinate of the contamination center, which follows a uniform distribution(`U(0,10)`)  
* `cont_level` = a vector that indicates the mean contamination level (CFU/g or CFU/mL) and the standard deviation, assuming contamination level follows a log normal distribution. 

** Mode 1: Discrete Spread** 

* `n_affected` = the number of affected plants near the contamination spot, which follows a Poisson distribution (`Pois(lambda = 5)`)   
* `covar_mat` = covariance matrix of `x` and `y`, which defines the spread of contamination. Assume the spread follows a 2D normal distribution with var(X) = 0.25, var(Y) = 0.25 and cov(X, Y) = 0  

** Mode 2: Continuous Spread**

* `spread_radius` = the radius of the contamination spread
* `LOC` = the limit of contribution of contamination. By default, it is set at 0.001.(Both `spread_radius` and `LOC` determine the shape of decay function that describes how much contamination from the source is contributed to a target point.)

```{r}
## The input parameters
n_contam = rpois(n = 1, lambda = 3)
x_lim = c(0, 10)
y_lim = c(0, 10)
cont_level = c(10^7, 10)

### Mode 1
n_affected = rpois(n = 1, lambda = 5)
covar_mat = matrix(data = c(0.25, 0, 0, 0.25), nrow = 2, ncol = 2)

### Mode 2
spread_radius = 2.5
LOC = 10^(-3)
```

```{r}
# Generate the coordinates of contamination points
contam_xy = sim_contam(n_contam = n_contam, xlim = x_lim, ylim = y_lim, covariance = covar_mat, n_affected = n_affected, radius = spread_radius, cont_level = cont_level) 
```

```{r}
## Basic info of the contamination simulation
str(contam_xy)

summary(contam_xy$label)
```


3. Define parameters for generating sampling plans.

* `n_sp` = the number of sampling points
* `sp_radius` = the radius (m) of a circular region around the sample point. (Only applicable to **Mode 1: Discrete Spread**)
* `n_strata` = the number of strata (applicable to *Stratified random sampling*)
* `by` = the side along which the field is divided into strata. It is either "row" or "column" (applicable to *Stratified random sampling*) **OR** the side along which a sample is taken every k steps (applicable to *Systematic sampling*).

```{r}
n_sp = 15
sp_radius = 1
n_strata = 5
by = "row"
```

4. Show all the functions that are necessary for generating sampling plans.


```{r}
# Create a helper function that gives unique identifers
naming_sp

# Create a function that calculates the boundaries of each stratum
calc_bounds

# Create a function that generates a simple random sampling plan
sim_plan_srs

# Create a function that generates a stratified random sampling plan
sim_plan_strs

# Create a function that generates a systematic sampling plan
sim_plan_ss

# Create a function that calculates the Euclidean distance between points and only outputs the distances between sample points and contamination points.
calc_dist

## Calculate the percent of contamination a source contributes to a sample point
calc_perc_contam

# Create a function that calculates contamination levels for each sample point and combine "contam_xy" and "sp_xy"
gen_sim_data
```

5. Generate a sampling plan.

    a) `method = "srs"` generates a simple random sampling plan with `n_sp` and `sp_radius`.
    
        i) Sample point coordinates follow a uniform distribution.

    b) `method = "strs"` generates a stratified random sampling plan with `n_sp`, `sp_radius`, `n_strata` and `by`.
    
        i) Check whether `n_sp` is a multiple of `n_strata`.
        
        ii) Divide the field into strata either by row or by column.
        
        iii) Within each stratum, sample point coordinates follow a uniform distribution.
    
    c) `method = "ss"` generates a systematic sampling plan with `n_sp`, `sp_radius` and `by`.
    
        i) Split the field into `N` unit squares ($N = length \times width$).
        
        ii) Calculate `k`. $k = \frac {N} {n_{sp}}$.
        
        iii) In the first unit square, randomly select a sample point whose coordinates follow a uniform distribution.
        
        iv) Generate the rest of the sample points either along the x-axis or y-axis with the equation: $$x = x_0 + (n-1)k, n = 1, 2, ..., n_{sp} $$
        
        v) Arrange the sample points so that they distribute evenly within the field.

```{r}
# Run this if we want reproducibility
#set.seed(123)
```

```{r}
sp_xy = sim_plan(method = "ss", n_sp = n_sp, xlim = x_lim, ylim = y_lim, radius = sp_radius, by = by, n_strata = n_strata)

str(sp_xy)
```

6. Combine the `sp_xy` and `contam_xy`.

    a) Calculate the Euclidean distance between sample points and contamination points. 
    
    b) Use the distance and f_exp() to calculate the contamination contribution from each contamination point.
    
    c) Sum up the contamination contribution from all source points for each sample point.
    
    d) Update the `cont_level` column for sample points by matching row numbers.

```{r}
contam_sp_xy = gen_sim_data(df_contam = contam_xy, df_sp = sp_xy, spread_radius = spread_radius, LOC = LOC, fun = "norm")
```

# Results

1. Show the simulated contamination.

```{r}
# Mode 1: Discrete Spread
plot_contam_dis = contam_draw(data = contam_xy, spread = "discrete", xlim = x_lim, ylim = y_lim)

plot_contam_dis

# Mode 2: Continuous Spread
plot_contam_cont = contam_draw(data = contam_xy, spread = "continuous", xlim = x_lim, ylim = y_lim)

plot_contam_cont
```

2. Show the sample points and sample regions.

```{r, echo = FALSE}
# Simple random sampling
# plot_sp_dis_srs = sp_draw_srs(data = sp_xy, spread = "discrete", xlim = x_lim, ylim = y_lim)
# 
# plot_sp_cont_srs = sp_draw_srs(data = sp_xy, spread = "continuous", xlim = x_lim, ylim = y_lim)
```

```{r, echo = FALSE}
# # Sampling plan for continuous spread
# plot_sp_dis_srs
# 
# # Sampling plan for discrete spread
# plot_sp_cont_srs
```

```{r, echo = FALSE}
# Stratified random sampling
# plot_sp_dis_strs = sp_draw(method = "strs", data = sp_xy, spread = "discrete", xlim = x_lim, ylim = y_lim, n_strata = n_strata, by = by)
# 
# plot_sp_cont_strs = sp_draw(method = "strs", data = sp_xy, spread = "continuous", xlim = x_lim, ylim = y_lim, n_strata = n_strata, by = by)
```

```{r, echo = FALSE}
# plot_sp_dis_strs
# 
# plot_sp_cont_strs
```

```{r}
# Systematic sampling
plot_sp_dis_ss = sp_draw(method = "ss", data = sp_xy, spread = "discrete", xlim = x_lim, ylim = y_lim, by = by)

plot_sp_cont_ss = sp_draw(method = "ss", data = sp_xy, spread = "continuous", xlim = x_lim, ylim = y_lim, by = by)
```

```{r}
plot_sp_dis_ss

plot_sp_cont_ss
```

3. Overlay the sampling plan on the simulated contamination plot.

```{r}
# Simple random sampling
# plot_overlay_cont = overlay_draw(method = "srs", data = contam_sp_xy, spread = "continuous", xlim = x_lim, ylim = y_lim)
# 
# plot_overlay_dis = overlay_draw(method = "srs", data = contam_sp_xy, spread = "discrete", xlim = x_lim, ylim = y_lim)
```

```{r}
# # Sampling plan for continuous spread
# plot_overlay_cont
# # 
# # # Sampling plan for discrete spread
# plot_overlay_dis
```

```{r}
# Stratified random sampling
# plot_overlay_dis_strs = overlay_draw(method = "strs", data = contam_sp_xy, spread = "discrete", xlim = x_lim, ylim = y_lim, n_strata = n_strata, by = by)
# 
# plot_overlay_cont_strs = overlay_draw(method = "strs", data = contam_sp_xy, spread = "continuous", xlim = x_lim, ylim = y_lim, n_strata = n_strata, by = by)
```

```{r}
# plot_overlay_dis_strs
# 
# plot_overlay_cont_strs
```

```{r}
# Systematic sampling
plot_overlay_dis_ss = overlay_draw(method = "ss", data = contam_sp_xy, spread = "discrete", xlim = x_lim, ylim = y_lim)

plot_overlay_cont_ss = overlay_draw(method = "ss", data = contam_sp_xy, spread = "continuous", xlim = x_lim, ylim = y_lim)
```

```{r}
plot_overlay_dis_ss

plot_overlay_cont_ss
```

