---
title: 'Sampling: Assay Preparation'
author: "Xianbin Cheng"
date: "February 22, 2019"
output: html_document
---

# Objective

  * Create a module that simulates taking analytical samples from work samples
  
# Method

1. Load libraries and source R code.

```{r, warning = FALSE, message = FALSE}
source(file = "Sampling_libraries.R")
source(file = "Sampling_contamination.R")
source(file = "Sampling_contamination_3d.R")
source(file = "Sampling_visualization.R")
source(file = "Sampling_assay_prep.R")
source(file = "Sampling_plan.R")
source(file = "Sampling_plan_3d.R")
```

2. List important parameters from `Sampling_contamination.R`.

* `n_contam` = the number of contamination points  
* `x_lim` = the limits of the x-axis  
* `y_lim` = the limits of the y-axis  
* `z_lim` = the limits of the z-axis
* `x` = the horizontal coordinate of the contamination center, which follows a uniform distribution by default
* `y` = the vertical coordinate of the contamination center, which follows a uniform distribution by default
* `z` = the vertical coordinate of the contamination center, which follows a uniform distribution by default
* `cont_level` = a vector that indicates the mean contamination level (logCFU/g or logCFU/mL) and the standard deviation in a log scale, assuming contamination level follows a log normal distribution $ln(cont\_level)$~$N(\mu, \sigma^2)$. 
* `dis_level` = a vector that indicates the mode (ppb) and the lower bound (ppb), assuming contamination level follows $lb+Gamma(\alpha, \theta=\frac {mode-20}{\alpha-1})$

** Mode 1: Discrete Spread** 

* `n_affected` = the number of affected kernels near the contamination spot, which follows a Poisson distribution ($Pois(\lambda = 5)$)   
* `covar_mat` = covariance matrix of `x` and `y`, which defines the spread of contamination. Assume the spread follows a 2D normal distribution with var(X) = 0.25, var(Y) = 0.25 and cov(X, Y) = 0   

** Model 2: Continuous Spread**

We do not consider such type of spread in a 3D space. 

```{r}
## The input parameters
n_contam = 3
x_lim = c(0, 8)
y_lim = c(0, 2)
z_lim = c(0, 2)
lims = list(xlim = x_lim, ylim = y_lim, zlim = z_lim)
cont_level = c(7, 1)
dis_level = c("mode"= 40000, "lb" = 20)
spread = "discrete"

### Discrete
n_affected = 2
covar_mat = make_covar_mat(spread = spread, varx = 0.25, vary = 0.25, varz = 0.25, covxy = 0, covxz = 0, covyz = 0)

### Continuous
spread_radius = 1
LOC = 10^(-3)
fun = "exp"
```

```{r}
# Run this if we want reproducibility
set.seed(123)
```

```{r, eval = FALSE}
# Generate the coordinates of contamination points
# Not run
contam_xy = sim_contam_new(n_contam = n_contam, lims = lims, spread = spread, covar = covar_mat, n_affected = n_affected, cont_level = cont_level, dis_level = dis_level) 
```

```{r}
## Test case
contam_xy = read.csv(file = "Test_case_truck.csv", row.names = 1, header = TRUE, stringsAsFactors = FALSE)
```

3. Define parameters for generating sampling plans.

* `method_sp` = sampling strategy, including `srs`, `strs`, `ss`.

**Mode 1: Continuous Spread**

* `n_sp` = the number of sampling points
* `n_strata` = the number of strata (applicable to *2D Stratified random sampling*)
* `by` = the side along which the field is divided into strata. It is either "row" or "column" (applicable to *2D Stratified random sampling*) **OR** the side along which a sample is taken every k steps (applicable to *2D Systematic sampling*).

**Mode 1: Discrete Spread**   

* `d` = inner diameter of the probe (m)
* `L` = length of the probe (m). It can be 5, 6, 8, 10, 12 feet, depending on the container type. Remember to convert it to meters. We assume it's fully inserted to the corn
* `rho` = average density of a kernel (g/cm3) (Beware of the unit when calculating mass)
* `m_kbar` = average mass of a kernel
* `container` = "truck", "barge", "hopper"
* `depth_ft` = the depth of corn inside the truck. There are two sampling patterns for trucks, depending on whether depth is higher than or lower than 4 ft.
* `compartment` and `type` = arguments for hopper cars. `compartment` can be 2 or 3, `type` can be `open_top` or `trough`.

```{r}
method_sp = "ss"

# Continuous
n_sp = 15
n_strata = 5
by = "row"

# Discrete
# sp_radius = 0.5 (This is theoretically for SRS and STRS)
container = "truck"
depth_ft = 5
#compartment = 2
#type = "open_top"

d = 0.5
L = get_Lprobe(container = container, lims = lims)
m_kbar = 0.3 #unit: g
rho = 1.28
```

```{r}
# Generate the coordinates of sample points
sp_xy = sim_plan_new(method_sp = "ss", spread = spread, lims = lims, radius = d/2, container = container)
```

4. Determine whether contaminated kernels are captured and calculate sample concentration in the probe. Also calculate the true contamination level in the container. 

  * Capture criteria:
  
    1) $d_{xy} \le d/2$, where $d_{xy}$ = 2D Euclidean distance between a sample point and a kernel on the X-Y plane, d = inner diameter of the probe;
    2) $z_i >= zlim[2] - L$, where $z_i$ = the z-coordinate of the kernel. We assume the probe is fully inserted into the bulk corn.

  * Healthy kernel distribution:
    
    Modified-PERT with min = 0, mode = 0.7, max = 19.99, shape = 80.
    
  * True contamination level in the container:
  
  $$C_{true}=\frac {(\sum_{i=1}^{k} C_{contam_i}+\sum_{j=1}^{n-k} C_{healthy_j})\times \bar m_k}{n\times \bar m_k}=\frac{(\sum_{i=1}^{k}C_{contam_i}+(n-k)\times \bar C_{healthy})}{n}$$

```{r}
# Pre-generate healthy kernel concentrations to save time
conc_neg = rpert(n = 10^6, min = 0, mode = 0.7, max = 19.99, shape = 80)
```

```{r}
# Generate the distance matrix
dist_contam_sp = calc_dist(df_contam = contam_xy, df_sp = sp_xy, spread = spread, method_sp = method_sp)

contam_sp_xy = gen_sim_data_new(df_contam = contam_xy, df_sp = sp_xy, dist = dist_contam_sp, spread = spread, sp_radius = d/2, L = L, rho = rho, m_kbar = m_kbar, conc_neg = conc_neg)
```

# Result

1. show the captured kernels.

```{r}
# Summary
kable_styling(kable_input = kable(contam_sp_xy$combined, format = "html"), full_width = FALSE)

# Captured kernels
contam_sp_xy$raw$kcap
```

2. 2D visualization.

```{r}
overlay_draw(method_sp = method_sp, data = contam_sp_xy$combined, spread = spread, xlim = lims$xlim, ylim = lims$ylim)
overlay_draw_probe(data = contam_sp_xy$combined, lims = lims, L = L)
```

3. Show the pooled sample distribution.

```{r}
temp = data.frame(conc = contam_sp_xy$raw$c_pooled) %>%
  mutate(class = ifelse(.$conc >= 20, yes = "H", no = "L"))

ggplot(data = temp, aes(x = conc, fill = class)) +
  geom_histogram(bins = 100) +
  scale_x_log10() +
  scale_y_sqrt() +
  theme_bw()
```

4.  Show the true contamination level.

```{r}
contam_sp_xy$c_true
```

