---
title: 'Sampling: Sampling Plan'
author: "Xianbin Cheng"
date: "September 7, 2018"
output: html_document
---

# Method

1. Load libraries and source R code.

```{r, warning = FALSE, message = FALSE}
source(file = "Sampling_libraries.R")
source(file = "Sampling_contamination.R")
source(file = "Sampling_visualization.R")
source(file = "Sampling_plan.R")
```

```{r}
sessionInfo()
```

2. List important parameters from `Sampling_contamination.R`.

* `n_contam` = the number of contamination points  
* `x_lim` = the limits of the horizontal axis  
* `y_lim` = the limits of the vertical axis  
* `x` = the horizontal coordinate of the contamination center, which follows a uniform distribution (`U(0,10)`)
* `y` = the vertical coordinate of the contamination center, which follows a uniform distribution(`U(0,10)`)  
* `cont_level` = a vector that indicates the mean contamination level (logCFU/g or logCFU/mL) and the standard deviation in a log scale, assuming contamination level follows a log normal distribution $ln(cont\_level)$~$N(\mu, \sigma^2)$.  

** Mode 1: Discrete Spread** 

* `n_affected` = the number of affected plants near the contamination spot, which follows a Poisson distribution (`Pois(lambda = 5)`)   
* `covar_mat` = covariance matrix of `x` and `y`, which defines the spread of contamination. Assume the spread follows a 2D normal distribution with var(X) = 0.25, var(Y) = 0.25 and cov(X, Y) = 0  

** Mode 2: Continuous Spread**

* `spread_radius` = the radius of the contamination spread
* `LOC` = the limit of contribution of contamination. By default, it is set at 0.001.(Both `spread_radius` and `LOC` determine the shape of decay function that describes how much contamination from the source is contributed to a target point.)
* `fun` = the decay function that describes the spread. It takes either "exp" or "norm".

```{r}
## The input parameters
n_contam = rpois(n = 1, lambda = 3)
x_lim = c(0, 10)
y_lim = c(0, 10)
cont_level = c(7, 1)

### Mode 1
n_affected = rpois(n = 1, lambda = 5)
covar_mat = matrix(data = c(0.25, 0, 0, 0.25), nrow = 2, ncol = 2)

### Mode 2
spread_radius = 2.5
LOC = 10^(-3)
fun = "exp"
```

```{r}
# Generate the coordinates of contamination points
contam_xy = sim_contam(n_contam = n_contam, xlim = x_lim, ylim = y_lim, covariance = covar_mat, n_affected = n_affected, radius = spread_radius, cont_level = cont_level) 
```

```{r}
## Basic info of the contamination simulation
str(contam_xy)

summary(contam_xy$label)
```


3. Define parameters for generating sampling plans.

* `n_sp` = the number of sampling points
* `sp_radius` = the radius (m) of a circular region around the sample point. (Only applicable to **Mode 1: Discrete Spread**)
* `n_strata` = the number of strata (applicable to *Stratified random sampling*)
* `by` = the side along which the field is divided into strata. It is either "row" or "column" (applicable to *Stratified random sampling*) **OR** the side along which a sample is taken every k steps (applicable to *Systematic sampling*).

**Mode 1: Discrete Spread**   
* `m_kbar` = averaged kernel weight (g)
* `m_sp` = the analytical sample weight (25 g)
* `conc_good` = concentration of toxin in healthy kernels

```{r}
n_sp = 15
sp_radius = 1
n_strata = 5
by = "row"

m_kbar = 0.3
m_sp = 25
conc_good = 0.1
```

4. Show all the functions that are necessary for generating sampling plans.


```{r}
# Create a helper function that gives unique identifers
naming_sp

# Create a function that calculates the boundaries of each stratum
calc_bounds

# Create a function that generates a simple random sampling plan
sim_plan_srs

# Create a function that generates a stratified random sampling plan
sim_plan_strs

# Create a function that generates a systematic sampling plan
sim_plan_ss

# Create a function that calculates the Euclidean distance between points and only outputs the distances between sample points and contamination points.
calc_dist

## Calculate the percent of contamination a source contributes to a sample point
calc_perc_contam

# Create a function that calculates contamination levels for each sample point and combine "contam_xy" and "sp_xy"
gen_sim_data
```

5. Generate a sampling plan.

    a) `method = "srs"` generates a simple random sampling plan with `n_sp` and `sp_radius`.
    
        i) Sample point coordinates follow a uniform distribution.

    b) `method = "strs"` generates a stratified random sampling plan with `n_sp`, `sp_radius`, `n_strata` and `by`.
    
        i) Check whether `n_sp` is a multiple of `n_strata`.
        
        ii) Divide the field into strata either by row or by column.
        
        iii) Within each stratum, sample point coordinates follow a uniform distribution.
    
    c) `method = "ss"` generates a systematic sampling plan with `n_sp`, `sp_radius` and `by`.
    
        i) Split the field into `N` unit squares ($N = length \times width$).
        
        ii) Calculate `k`. $k = \frac {N} {n_{sp}}$.
        
        iii) In the first unit square, randomly select a sample point whose coordinates follow a uniform distribution.
        
        iv) Generate the rest of the sample points either along the x-axis or y-axis with the equation: $$x = x_0 + (n-1)k, n = 1, 2, ..., n_{sp} $$
        
        v) Arrange the sample points so that they distribute evenly within the field.

```{r}
# Run this if we want reproducibility
#set.seed(123)
```

```{r}
sp_xy = sim_plan(method = "ss", n_sp = n_sp, xlim = x_lim, ylim = y_lim, radius = sp_radius, by = by, n_strata = n_strata)

str(sp_xy)
```

6. Calculate the contamination level of the sample points. Combine the `sp_xy` and `contam_xy`.

    1) Calculate the Euclidean distance between sample points and contamination points. 
    
    a) **Discrete Spread:**
    
        i) Use the distance to keep the sample points that fall within `sp_radius`.
        
        ii) Calculate the contamination level of each sample point.
        
        $$C_i = \frac {\sum \limits_{j=1}^n C_{ij}\times \bar{m_{k}}} {m_{sp}} = \frac {\bar {m_k}} {m_{sp}} \times [C_{i1} + C_{i2} + ... + C_{ik} + (n_k - k)\times C_{good}] $$ 
        
        , where $C_i$ = contamination level of `sample point i`, 
                        
        $C_{ij}$ = contamination level of `kernel j` in `sample point i`,
        
        $\bar m_k$ = averaged weight of a single kernel,
        
        $m_{sp}$ = weight of an analytical unit,
                        
        $n_k$ = the total number of kernels in an analytical unit, calculated by $\frac {m_{sp}} {\bar m_k}$,
                        
        $k$ = the number of contamination spots or spreads in this sample,
                        
        $C_{good}$ = background contamination level.
        
    b) **Continuous Spread:**
    
        i) Use the distance and decay function to calculate the contamination contribution from each contamination point.
        
        ii) Sum up the contamination contribution from all source points for each sample point.
        
        $$C_{sp_i} = \sum \limits_{j=1}^n C_{cpj} \times f(d_{ij}) =  C_{cp1}\times f(d_{i1})+ C_{cp2}\times f(d_{i2})+ ...+C_{cpn}\times f(d_{in})$$ 
        
        , where $C_{sp_i}$ = contamination level of `sample point i`,  
        
        $C_{cpj}$ = contamination level of `contamination point j` (`j` = 1, 2, ..., n),   
        
        $d_{ij}$ = distance between `sample point i` and `contamination point j`,
        
        `f()` = decay function that calculates the contribution of contamination.
        
    2) Add in sampling error to the sample points for the continuous spread case, assuming the sampling error follows a log normal distribution with mean = 0 and sd = 1. 
        
    $$C_{sp\_with\_error_i}=C_{sp_i}+\epsilon_i$$
    , where $i = 1,2,...,n_{sp}$; $ln(\epsilon)$~$N(\mu=0, \sigma^2 =1)$ 

```{r, eval = FALSE, echo = FALSE}
# gen_sim_data = function(df_contam, df_sp, dist, spread_radius, sp_radius, LOC, fun, m_kbar, m_sp, conc_good){
# 
#   ### Calculate the cont_level (continuous spread)
#     # Subset the dist_contam_sp to keep the rows that show distance between spots and sample points
#     # Calculate the percent contribution based on distance
#     # Attach the source contamination level
#     # Calculate the contamination level at each sample point, which is source level * percent contribution
#     #Sum up the source_contri for each sample point to represent the actual contamination level at that sample point
# 
#   a = dist %>%
#     dplyr::filter(.data = ., label == "spot") %>%
#     mutate(perc_contri = calc_perc_contam(df_dist = ., r = spread_radius, LOC = LOC, fun = fun),
#            source_level = df_contam$cont_level[match(x = .$ID_contam, table = df_contam$ID)],
#            source_contri = source_level * perc_contri) %>%
#     group_by(ID_sp) %>%
#     summarise(cont_level = sum(source_contri))
# 
#   ### Calculate the dis_level (discrete spread)
#     # Estimate the number of kernels in each sample
# 
#   n_k = round(x = m_sp/m_kbar, digits = 0)
# 
#     # Subset the dist_contam_sp to keep rows where the contamination points fall within the sampling region
#     # Attach the source contamination level
#     # Calculate the sum of contamination point levels in each sample, and record the number of points in each sample
#     # Calculate the dis_level in each sample
# 
#   b = dist %>%
#     dplyr::filter(Distance <= sp_radius) %>%
#     mutate(source_level = df_contam$dis_level[match(x = .$ID_contam, table = df_contam$ID)]) %>%
#     group_by(ID_sp) %>%
#     summarise(obs = n(),
#               sum_level = sum(source_level)) %>%
#     mutate(dis_level = m_kbar/m_sp*(sum_level + (n_k - obs) * conc_good))
# 
#   ### Define sampling error
#   c = rlnorm(n = nrow(df_sp), meanlog = 0, sdlog = 1)
# 
#   ### Combine everything, fill the NAs with the corresponding contamination level.
#   df = rbind(df_contam, df_sp)
# 
#   # Add sampling error
#   df$cont_level[match(x = a$ID_sp, table = df$ID)] = a$cont_level #+ c
#   df$dis_level[match(x = b$ID_sp, table = df$ID)] = b$dis_level #+ c[length(b$dis_level)]
# 
#   if(anyNA(df$dis_level)){
#     df$dis_level[is.na(df$dis_level)] = conc_good
#   }
# 
#   return(df)
# }
```

```{r}
dist_contam_sp = calc_dist(df_contam = contam_xy, df_sp = sp_xy)

contam_sp_xy = gen_sim_data(df_contam = contam_xy, df_sp = sp_xy, dist = dist_contam_sp, spread_radius = spread_radius, sp_radius = sp_radius, LOC = LOC, fun = fun, m_kbar = m_kbar, m_sp = m_sp, conc_good = conc_good)
```

```{r}
kable_styling(kable(x = contam_sp_xy, format = "html"), full_width = FALSE)
```


# Results

1. Show the simulated contamination.

```{r, eval = FALSE}
# Mode 1: Discrete Spread
plot_contam_dis = contam_draw(data = contam_xy, spread = "discrete", xlim = x_lim, ylim = y_lim)

plot_contam_dis

# Mode 2: Continuous Spread
plot_contam_cont = contam_draw(data = contam_xy, spread = "continuous", xlim = x_lim, ylim = y_lim)

plot_contam_cont
```

2. Show the sample points and sample regions.

```{r, eval = FALSE}
# Systematic sampling
plot_sp_dis_ss = sp_draw(method = "ss", data = sp_xy, spread = "discrete", xlim = x_lim, ylim = y_lim, by = by)
plot_sp_cont_ss = sp_draw(method = "ss", data = sp_xy, spread = "continuous", xlim = x_lim, ylim = y_lim, by = by)

plot_sp_dis_ss
plot_sp_cont_ss
```

3. Overlay the sampling plan on the simulated contamination plot.

```{r}
# Systematic sampling
plot_overlay_dis_ss = overlay_draw(method = "ss", data = contam_sp_xy, spread = "discrete", xlim = x_lim, ylim = y_lim)

plot_overlay_cont_ss = overlay_draw(method = "ss", data = contam_sp_xy, spread = "continuous", xlim = x_lim, ylim = y_lim)
```

```{r}
plot_overlay_dis_ss

plot_overlay_cont_ss
```

```{r}
contam_level_draw(dimension = "3d", method = fun, spread_radius = spread_radius, LOC = LOC, df_contam = contam_xy, xlim = x_lim, ylim = y_lim, interactive = FALSE)
```
