---
title: 'Sampling: Assay Preparation'
author: "Xianbin Cheng"
date: "February 22, 2019"
output: html_document
---

# Objective

  * Create a module that simulates taking analytical samples from work samples
  
# Method

1. Load libraries and source R code.

```{r, warning = FALSE, message = FALSE}
source(file = "Sampling_libraries.R")
source(file = "Sampling_contamination.R")
source(file = "Sampling_visualization.R")
source(file = "Sampling_plan.R")
source(file = "Sampling_plan_3d.R")
```

2. List important parameters from `Sampling_contamination.R`.

* `n_contam` = the number of contamination points  
* `x_lim` = the limits of the x-axis  
* `y_lim` = the limits of the y-axis  
* `z_lim` = the limits of the z-axis
* `x` = the horizontal coordinate of the contamination center, which follows a uniform distribution by default
* `y` = the vertical coordinate of the contamination center, which follows a uniform distribution by default
* `z` = the vertical coordinate of the contamination center, which follows a uniform distribution by default
* `cont_level` = a vector that indicates the mean contamination level (logCFU/g or logCFU/mL) and the standard deviation in a log scale, assuming contamination level follows a log normal distribution $ln(cont\_level)$~$N(\mu, \sigma^2)$. 

** Mode 1: Discrete Spread** 

* `n_affected` = the number of affected kernels near the contamination spot, which follows a Poisson distribution ($Pois(\lambda = 5)$)   
* `covar_mat` = covariance matrix of `x` and `y`, which defines the spread of contamination. Assume the spread follows a 2D normal distribution with var(X) = 0.25, var(Y) = 0.25 and cov(X, Y) = 0   

** Model 2: Continuous Spread**

We do not consider such type of spread in a 3D space. 

```{r}
## The input parameters
n_contam = 3
x_lim = c(0, 30)
y_lim = c(0, 10)
z_lim = c(0, 2.5)
lims = list(xlim = x_lim, ylim = y_lim, zlim = z_lim)
cont_level = c(7, 1)
spread = "discrete"

### Discrete
n_affected = 2
covar_mat = make_covar_mat(spread = spread, varx = 0.25, vary = 0.25, varz = 0.25, covxy = 0, covxz = 0, covyz = 0)

### Continuous
spread_radius = 1
LOC = 10^(-3)
fun = "exp"
```

```{r}
# Run this if we want reproducibility
set.seed(123)
```

```{r}
# Generate the coordinates of contamination points
contam_xy = sim_contam_new(n_contam = n_contam, lims = lims, spread = spread, covar = covar_mat, n_affected = n_affected, spread_radius = spread_radius, cont_level = cont_level) 
```



# Result