---
title: 'Sampling: Assay'
author: "Xianbin Cheng"
date: "October 31, 2018"
output: html_document
---

# Method

1. Load libraries and source R code.

```{r, message = FALSE, warning = FALSE}
source("Sampling_libraries.R")
source("Sampling_contamination.R")
source("Sampling_plan.R")
source("Sampling_visualization.R")
source("Sampling_assay.R")
```

```{r}
sessionInfo()
```

2. List important parameters from `Sampling_contamination.R` and `Sampling_plan.R`.

**Contamination:**  

  * `n_contam` = the number of contamination points 
  * `x_lim` = the limits of the horizontal axis  
  * `y_lim` = the limits of the vertical axis  
  * `x` = the horizontal coordinate of the contamination center, which follows a uniform distribution (`U(0,10)`)
  * `y` = the vertical coordinate of the contamination center, which follows a uniform distribution(`U(0,10)`)  
  * `cont_level` = a vector that indicates the mean contamination level (logCFU/g or logCFU/mL) and the standard deviation in a log scale, assuming contamination level follows a log normal distribution $ln(cont\_level)$~$N(\mu, \sigma^2)$. 

  **Mode 1: Discrete Spread** 

  * `n_affected` = the number of affected plants near the contamination spot, which follows a Poisson distribution (`Pois(lambda = 5)`)   
  * `covar_mat` = covariance matrix of `x` and `y`, which defines the spread of contamination. Assume the spread follows a 2D normal distribution with var(X) =     0.25, var(Y) = 0.25 and cov(X, Y) = 0  

  **Mode 2: Continuous Spread**

  * `spread_radius` = the radius of the contamination spread. 
  * `LOC` = the limit of contribution of contamination. By default, it is set at 0.001.(Both `spread_radius` and `LOC` determine the shape of decay function that describes how much contamination from the source is contributed to a target point.)
  * `fun` = the decay function that describes the spread. It takes either "exp" or "norm".

**Sampling Plan:**  
  
  * `method_sp` = the sampling method (SRS, STRS, SS)
  * `n_sp` = the number of sampling points
  * `sp_radius` = the radius (m) of a circular region around the sample point. (Only applicable to **Mode 1: Discrete Spread**)
  * `n_strata` = the number of strata (applicable to *Stratified random sampling*)
  * `by` = the side along which the field is divided into strata. It is either "row" or "column" (applicable to *Stratified random sampling*) **OR** the side along which a sample is taken every k steps (applicable to *Systematic sampling*).
  * `m_kbar` = averaged kernel weight (g). By default, it's 0.3 g (estimated from Texas corn).
  * `m_sp` = the analytical sample weight (25 g)
  * `conc_good` = concentration of toxin in healthy kernels

```{r}
## Contamination
n_contam = rpois(n = 1, lambda = 3)
x_lim = c(0, 10)
y_lim = c(0, 10)
cont_level = c(7, 1)

### Mode 1
n_affected = rpois(n = 1, lambda = 5)
covar_mat = matrix(data = c(0.25, 0, 0, 0.25), nrow = 2, ncol = 2)

### Mode 2
spread_radius = 2.5
LOC = 10^(-3)
fun = "exp"

## Sampling plan
method_sp = "srs"
n_sp = 10
sp_radius = 1
n_strata = 5
by = "row"
m_kbar = 0.3
m_sp = 25
conc_good = 0.1
```

3. Generate the simulation dataset.

```{r}
# Generate the coordinates of contamination points
contam_xy = sim_contam(n_contam = n_contam, xlim = x_lim, ylim = y_lim, covariance = covar_mat, n_affected = n_affected, radius = spread_radius, cont_level = cont_level) 

# Generate the coordinates of sample points
sp_xy = sim_plan(method_sp = method_sp, n_sp = n_sp, xlim = x_lim, ylim = y_lim, radius = sp_radius, by = by)

# Generate the distance matrix
dist_contam_sp = calc_dist(df_contam = contam_xy, df_sp = sp_xy)

# Combine contam_xy and sp_xy
contam_sp_xy = gen_sim_data(df_contam = contam_xy, df_sp = sp_xy, spread_radius = spread_radius, LOC = LOC, fun = fun, dist = dist_contam_sp, sp_radius = sp_radius, m_kbar = m_kbar, m_sp = m_sp, conc_good = conc_good, cont_level = cont_level)
```

```{r}
str(contam_sp_xy)

summary(contam_sp_xy$label)
```

4. Define parameters.
  
  * `method_det` = method of detection  
      + Plating: LOD = 2500 CFU/g  
      + Enrichment: LOD = 1 CFU/g  
      + ELISA: LOD = 1 ng/g (Helica Total Aflatoxins ELISA kit)  
  
  **Mode 1: Discrete Spread:**  
      * `Mc` = maximum concentration limit of mycotoxin (ng/g or ppb)
  
  **Mode 2: Continuous Spread:**  
      * `case` = 1 ~ 15 cases that define the stringency of the sampling plan.  
      * Attributes plans:  
          + `n` = number of analytical units (25g)  
          + `c` = maximum allowable number of analytical units yielding positive results  
          + `m` = microbial count or concentration above which an analytical unit is considered positive  
          + `M` = microbial count or concentration, if any analytical unit is above `M`, the lot is rejected.  
      
```{r}
get_attr_plan

get_LOD
```

```{r}
# Define parameters: e.g. S.aureus in shrimps
case = 9
m = 50
M = 500

# Aflatoxin
Mc = 20

# Detection method: plating, enrichment, ELISA aflatoxin
method_det = "ELISA aflatoxin"
```

```{r}
# Attribute plan
get_attr_plan(case = case, m = m, M = M)

# LOD
get_LOD(method_det = method_det)
```

5. Decision: accept or reject lot.

```{r}
decision_cont
decision_dis
lot_decision
words
```

# Result

1. The data of sample points.

```{r}
kable_styling(kable(x = subset(x = contam_sp_xy, subset = label == "sample point"), format = "html"), full_width = FALSE)
```

2. Visualization.

```{r, fig.keep = TRUE, size = "50%"}
overlay_draw(method = method_sp, data = contam_sp_xy, spread = "continuous", xlim = x_lim, ylim = y_lim, n_strata = n_strata, by = by)
overlay_draw(method = method_sp, data = contam_sp_xy, spread = "discrete", xlim = x_lim, ylim = y_lim, n_strata = n_strata, by = by)
```

3. Decision.

*Continuous spread*  

```{r}
assay_draw(df = contam_sp_xy, M = M, m = m, method_det = method_det, Mc = Mc, spread = "continuous", case = case)
deci_cont = lot_decision(data = contam_sp_xy, case = case, m = m, M = M, method_det = method_det, Mc = Mc, spread = "continuous")
words(x = deci_cont)
```

*Discrete spread*  

```{r}
assay_draw(df = contam_sp_xy, M = M, m = m, method_det = method_det, Mc = Mc, spread = "discrete")
deci_dis = lot_decision(data = contam_sp_xy, case = case, m = m, M = M, method_det = method_det, Mc = Mc, spread = "discrete")
words(x = deci_dis)
```

