---
title: "Sampling 3D Simulation v4"
author: "Xianbin Cheng"
date: "09/17/2020"
output: html_document
---

# Objective

  To analyze data from 10,000 iterations of 3D simulation in a 3m x 2m x 1.5m truck (without parallelization).
  
# Method

1. Necessary inputs

```{r, warning = FALSE, message = FALSE}
library(kableExtra)
library(sensitivity)
source(file = "Sampling_libraries.R")
source(file = "Sampling_contamination.R")
source(file = "Sampling_contamination_3d.R")
source(file = "Sampling_visualization.R")
source(file = "Sampling_assay_prep.R")
source(file = "Sampling_plan.R")
source(file = "Sampling_plan_3d.R")
source(file = "Sampling_assay_3d.R")
source(file = "Sampling_assay.R")
source(file = "Sampling_outcome_3d.R")
source(file = "Sampling_outcome.R")
source(file = "Sampling_iteration.R")
source(file = "Sampling_tuning_3d.R")
source(file = "Sampling_analysis.R")
```

```{r}
# Important parameters
homogeneity = 0.1
Mc = 20

# Iteration
n_iter = 100
n_seed = 100

# Parameter tuning
c_hat_vec = c(5, 10, 20, 40, 80, 100)
n_affected_vec = c(1, 10, 100, 1000)
n_sp_vec = c(5, 10, 100)
method_sp_vec = c("srs", "strs", "ss")
```

2. Load all the RDS files and clean them up.

```{r, echo = FALSE}
f_clean_up = function(data, vals_prim, vals_sec, vals_tert, n_seed){

  # Clean up the data on the secondary tuning level
  a = map(.x = data, .f = metrics_dis_sec, vals_prim = vals_prim, vals_sec = vals_sec, n_seed = n_seed) %>%
    bind_rows()

  # Create a vector that specifies the tertiary tuning level
  b = as.character(rep(x = vals_tert, each = length(vals_prim) * length(vals_sec) * n_seed))

  # Combine
  return(data.frame(a, param3 = b, stringsAsFactors = FALSE))
}
```

```{r, eval = FALSE}
# Get the RDS file names
rds_files = dir(path = paste0(getwd(), "/RDS/3D Simulation"),pattern = "3x2x1.5", full.names = TRUE)

# Read rds files
exp1 = map(.x = str_subset(string = rds_files, pattern = "srsxstrsxss"), .f = readRDS)
exp2 = map(.x = str_subset(string = rds_files, pattern = "srsxstrsxss", negate = TRUE), .f = readRDS)

# Clean up the rds files into csv files
exp1_cleaned = f_clean_up(data = exp1, vals_prim = c_hat_vec, vals_sec = method_sp_vec, vals_tert = n_affected_vec, n_seed = n_seed)

exp2_cleaned = f_clean_up(data = exp2, vals_prim = c_hat_vec, vals_sec = n_sp_vec, vals_tert = n_affected_vec, n_seed = n_seed)
```

```{r, echo = FALSE, message = FALSE}
exp1_cleaned = read.csv(file = "sim_3x2x1.5_exp1_7_srsxstrsxss_1x10x100x1000_100x100.csv", header = TRUE, row.names = 1, stringsAsFactors = FALSE)
exp2_cleaned = read.csv(file = "sim_3x2x1.5_exp2_5x10x100_srs_1x10x100x1000_100x100.csv", header = TRUE, row.names = 1, stringsAsFactors = FALSE)
```

```{r, echo = FALSE}
exp_names = tibble(experiment = c(1,2), 
                   c_hat = rep(x = str_c(c_hat_vec, collapse = ","), times = 2), 
                   homogeneity = rep(homogeneity, 2), 
                   n_sp = c("7", str_c(as.character(n_sp_vec), collapse = ",")), 
                   method_sp = c(str_c(method_sp_vec, collapse = ","), "srs"), 
                   n_affected = rep(str_c(as.character(n_affected_vec), collapse = ","), times = 2), 
                   n_seed = rep(n_seed, times = 2), 
                   n_iter = rep(n_iter, times = 2))

kable_styling(kable_input = kable(x = exp_names, format = "html"), full_width = TRUE)
```

2. Further summarizing of the data to produce OC curves

```{r, echo = FALSE}
# Combine two experiments
f_combine = function(data1, data2, exp1_param, exp2_param){
  
  a = data1 %>%
    rename(.data = ., "method_sp" = "param2", "c_hat" = "param", "n_affected" = "param3") %>%
    mutate(experiment = 1, n_sp = exp1_param) %>%
    dplyr::select(experiment, seed, P_rej, Paccept, c_true, c_hat, n_sp, method_sp, n_affected)
  
  b = data2 %>%
    rename(.data = ., "n_sp" = "param2", "c_hat" = "param", "n_affected" = "param3") %>%
    mutate(experiment = 2, method_sp = exp2_param) %>%
    dplyr::select(experiment, seed, P_rej, Paccept, c_true, c_hat, n_sp, method_sp, n_affected)
    
  return(rbind.data.frame(a, b))
}
```

```{r}
exp_combined = f_combine(data1 = exp1_cleaned, data2 = exp2_cleaned, exp1_param = 7, exp2_param = "srs")
```

3. Sensitivity analysis

```{r}
# Experiment all
sens_all = sensitivity::pcc(X = subset(x = exp_combined, select = c("method_sp", "n_affected", "n_sp", "c_hat")), 
                            y = exp_combined$Paccept, 
                            rank = TRUE, 
                            nboot = 100, 
                            conf = 0.95)
```

4. ANOVA for `Paccept` ~ `method_sp`/`n_sp` under different `n_affected`

```{r, echo = FALSE}
# ANOVA pvalues
get_pval = function(data, form){
  a = data %>%
    dplyr::filter(param == 20)
  b = aov(formula = form, data = a) %>%
    summary() 
  return(b[[1]]$`Pr(>F)`[1])
}
```

```{r}
pval1 = split(x = exp1_cleaned, f = exp1_cleaned$param3) %>%
  map(.x = ., .f = get_pval, form = Paccept ~ as.factor(param2))

pval2 = split(x = exp2_cleaned, f = exp2_cleaned$param3) %>%
  map(.x = ., .f = get_pval, form = Paccept ~ as.factor(param2))

pval_all = rbind.data.frame(bind_cols(pval1), bind_cols(pval2)) %>%
  mutate(experiment = c(1, 2), formula = c("Paccept ~ as.factor(method_sp)", "Paccept ~ as.factor(n_sp)"), c_hat = 20) %>%
  gather(data = ., key = "n_affected", value = "p.value", -c(experiment, formula, c_hat)) %>%
  dplyr::arrange(experiment)
```

# Results

```{r, echo = FALSE}
plot_tornado = function(data, param_labels){
  
  a = rownames_to_column(.data = data$PRCC, var = "Variable")
  a$Variable = fct_inorder(f = a$Variable)
  colnames(a)[4:6] = c("std_error", "min_ci", "max_ci")
  
  ggplot(data = a) +
    geom_crossbar(aes(x = Variable, y = original, ymin = min_ci, ymax = max_ci)) +
    geom_hline(yintercept = 0, color = "red") +
    scale_x_discrete(labels = param_labels) +
    scale_y_continuous(breaks = seq(-1, 1, 0.2)) +
    labs(x = "Variables", y = "PRCC index") +
    coord_flip(ylim = c(-1, 1)) +
    theme_bw()
}

plot_tune3 = function(data, xlab, legend_lab){
  
  a = data %>% 
    gather(data = ., key = "metric", value = "value", -c(seed, param, param2, param3)) %>% 
    group_by(param3, param2, param, metric) %>% 
    summarise(lb = quantile(x = value, probs = 0.025), med = median(x = value), 
              ub = quantile(x = value, probs = 0.975)) %>% 
    dplyr::filter(metric == "Paccept")
  
  b = ggplot(data = a) + 
    geom_ribbon(aes(x = param, ymin = lb, 
                    ymax = ub, group = as.factor(param2), 
                    fill = as.factor(param2)), 
                alpha = 0.3) + 
    geom_line(aes(x = param, y = med, color = as.factor(param2))) + 
    geom_point(aes(x = param, y = med, color = as.factor(param2))) + 
    scale_y_continuous(breaks = seq(from = 0, to = 1, by = 0.1)) + 
    scale_fill_discrete(name = legend_lab) + 
    scale_color_discrete(name = legend_lab) + 
    coord_cartesian(ylim = c(0, 1)) + 
    labs(x = xlab, y = "Probability of acceptance (2.5th - 97.5th percentile)") + 
    facet_wrap(param3 ~ .) +
    theme_bw() + 
    theme(legend.position = "top")
    
  return(b)
}

vis_diag = function(data){
  a = data %>% 
    gather(data = ., key = "metric", value = "value", -c(seed, param, param2, param3)) %>% 
    group_by(param3, param2, param, metric) %>% 
    summarise(lb = quantile(x = value, probs = 0.025), med = median(x = value), 
              ub = quantile(x = value, probs = 0.975)) %>% 
    dplyr::filter(metric == "c_true")
    
  ggplot(data = a) +
      geom_ribbon(aes(x = param, ymin = lb, ymax = ub, group = as.factor(param2), fill = as.factor(param2)), 
                  alpha = 0.3) +
      geom_line(aes(x = param, y = med, color = as.factor(param2))) +
      geom_point(aes(x = param, y = med, color = as.factor(param2))) +
      geom_abline(slope = 1,intercept = 0, color = "red") +
      # scale_x_log10(breaks = c(5, seq(10, 100, 10))) +
      # scale_y_continuous(breaks = seq(from = 0, to = 1, by = 0.1)) +
      # coord_cartesian(ylim = c(0,1)) +
      labs(x = "Input concentration (ppb)", y = "Output concentration (2.5th - 97.5th percentile)") +
      theme_bw() +
      facet_wrap(~ param3) +
      theme(legend.position = "top")
}
```

1. Visualization: Experiment 1

```{r, echo = FALSE}
plot_tune3(data = exp1_cleaned, xlab = "Estimated aflatoxin concentration (ppb)", legend_lab = "Sampling strategy")
```

2. Visualization: Experiment 2

```{r, echo = FALSE}
plot_tune3(data = exp2_cleaned, xlab = "Estimated aflatoxin concentration (ppb)", legend_lab = "Number of samples")
```

3. Sensitivity tornado plot

```{r, echo = FALSE}
sens_all
plot_tornado(data = sens_all, param_labels = c("Sampling strategy", "Clustering", "Number of probes", "Aflatoxin concentration"))
```

4. ANOVA results

```{r, echo = FALSE}
kable_styling(kable_input = kable(pval_all, format = "html"), full_width = TRUE)
```

5. Quality control figures that show how much the output concentration deviates from the input concentration.

```{r, echo = FALSE}
vis_diag(data = exp1_cleaned)
vis_diag(data = exp2_cleaned)
```


# Appendix

```{r, echo = FALSE}
sessionInfo()
```

