---
title: "Validation Discrete Mode"
author: "Xianbin Cheng"
date: "September 24, 2019"
output: html_document
---

# Objective

  Use Whitaker's data to validate our 3D model.
  
# Method

###1. Load libraries and source R code.

```{r, warning = FALSE, message = FALSE}
source(file = "Sampling_libraries.R")
source(file = "Sampling_contamination.R")
source(file = "Sampling_contamination_3d.R")
source(file = "Sampling_visualization.R")
source(file = "Sampling_assay_prep.R")
source(file = "Sampling_plan.R")
source(file = "Sampling_plan_3d.R")
source(file = "Sampling_assay_3d.R")
source(file = "Sampling_assay.R")
source(file = "Sampling_outcome_3d.R")
source(file = "Sampling_outcome.R")
source(file = "Sampling_iteration.R")
source(file = "Sampling_tuning_3d.R")
source(file = "Sampling_analysis.R")
source(file = "Validation.R")
library(lme4)
```

###2. List important parameters.

  * Whitaker's experimental conditions:
      + Total corn mass = 100 lbs
      + Container: presumedly a cube
      + `dis_level` = distribution of aflatoxin concentration in contaminated kernels. Assume it's a constant.
      + `homogeneity` = degree of grinding.
      + Contaminated kernels distribution: We assume they distribution uniformly in the container.

```{r}
# Pre-generate healthy kernel concentrations to save time
conc_neg = rpert(n = 10^6, min = 0, mode = 0.7, max = 19.99, shape = 80)
```

```{r}
## Contamination
m_kbar = 0.3 
rho = 1.28
cube_side = get_cube_side(pound = 100, rho = rho)
x_lim = c(0, cube_side)
y_lim = c(0, cube_side)
z_lim = c(0, cube_side)
lims = list(xlim = x_lim, ylim = y_lim, zlim = z_lim)

c_hat = 10
dis_level = list(type = "constant", args = 40000)
#dis_level = list(type = "Gamma", args = list("mode"= 40000, "lb" = 20))
spread = "discrete"
n_affected = 0
covar_mat = make_covar_mat(spread = spread, varx = 0.0009, vary = 0.0009, varz = 0.0009, 
                           covxy = 0, covxz = 0, covyz = 0)

# Sampling
homogeneity = 0.6

# Randomness
seed = NA
```

###3. Produce simulated data and run ANOVA with random effects

  * `n` = Number of test samples (32)
  * `n_sub` = Number of subsamples per test sample (2)
  * `m_sp` = mass of subsample (50g)
  * `unbalanced` = indicator for unbalanced design
  * `Mc` = mycotoxin threshold level (ng/g)
  * `c_hat_vec` = vector containing all the aflatoxin concentrations in Whitaker's data

```{r}
n = 32
n_sub = 2
m_sp = 50
unbalanced = FALSE
Mc = 20

c_hat_vec = c(5.8, 6.4, 6.7, 8.6, 11.8, 15.9, 18.2, 25.6, 27.3, 32.9, 56.7, 57.1, 94.7, 95.6, 113.8, 276.9, 298.9, 676.6)
```

```{r}
# Generate simulation data
sim_data = sim_intmed_dis_val(c_hat = c_hat, rho = rho, m_kbar = m_kbar, 
                              conc_neg = conc_neg, lims = lims, covar = covar_mat,
                              spread = spread, n_affected = n_affected, 
                              dis_level = dis_level, seed = seed, n = n, m_sp = m_sp, 
                              n_sub = n_sub, homogeneity = homogeneity, unbalanced = unbalanced)

str(sim_data$df)
```

```{r}
# ANOVA
summary(lmer(formula = value ~ 1 + (1|test_sp), data = sim_data$df, REML = TRUE))
```

###5. Wrap things up into a single function and run the function for all the concentrations

```{r}
# Wrap arguments into one single list
ArgList_default = list(c_hat = c_hat, lims = lims, spread = spread, covar_mat = covar_mat,
                       n_affected = n_affected, dis_level = dis_level, n = n, 
                       rho = rho, m_kbar = m_kbar, conc_neg = conc_neg, homogeneity = homogeneity, 
                       m_sp = m_sp, n_sub = n_sub, unbalanced = unbalanced, Mc = Mc)

n_seed = 10
n_iter = 10
```

```{r}
result = map(.x = c_hat_vec, .f = tune_param_val, Args = ArgList_default, n_seed = n_seed, n_iter = n_iter, param = "c_hat")
```

```{r}
result_cleaned = metrics_dis_n_val(data = result)
str(result_cleaned)
```

# Result


```{r, echo = FALSE}
f_vis = function(data, type, Mc){
  
  a = data %>%
    group_by(param, metrics) %>%
    summarise(lb = quantile(x = value, probs = 0.025), 
              med = median(x = value),
              ub = quantile(x = value, probs = 0.975))
  
  
  if(type == "diag"){
    
    # This shows comparison between c_test, c_true, and c_hat
    b = a %>%
      dplyr::filter(.data = ., metrics %in% c("c_test", "c_true"))
    
    ggplot(data = b) +
      geom_ribbon(aes(x = param, ymin = lb, ymax = ub, fill = metrics), alpha = 0.3) +
      geom_line(aes(x = param, y = med, color = metrics)) +
      geom_point(aes(x = param, y = med, color = metrics)) +
      scale_color_discrete(name = "Type", labels = c("Test concentration", "True concentration")) +
      scale_fill_discrete(name = "Type", labels = c("Test concentration", "True concentration")) +
      labs(x = "Input concentration (ppb)", y = "Output concentration (2.5th - 97.5th percentile)") +
      theme_bw() +
      theme(legend.position = "top")
      
  } else if(type == "var"){
    
    # This shows variance components var_sub, var_test VS c_hat
    c = a %>%
      dplyr::filter(.data = ., metrics %in% c("var_sub", "var_test"))
    
    ggplot(data = c) +
      geom_ribbon(aes(x = param, ymin = lb, ymax = ub, fill = metrics), alpha = 0.3) +
      geom_line(aes(x = param, y = med, color = metrics)) +
      geom_point(aes(x = param, y = med, color = metrics)) +
      scale_color_discrete(name = "Type", labels = c("Subsample", "Test sample")) +
      scale_fill_discrete(name = "Type", labels = c("Subsample", "Test sample")) +
      labs(x = "Input concentration (ppb)", y = "Variance component (2.5th - 97.5th percentile)") +
      theme_bw() +
      theme(legend.position = "top")
    
  } else if (type == "OC"){
    
    # This plots Paccept against c_hat
    d = a %>%
      dplyr::filter(.data = ., metrics == "Paccept")
    
    ggplot(data = d) +
      geom_ribbon(aes(x = param, ymin = lb, ymax = ub), alpha = 0.3) +
      geom_line(aes(x = param, y = med)) +
      geom_point(aes(x = param, y = med)) +
      geom_vline(xintercept = Mc, color = "red") +
      scale_x_log10() +
      coord_cartesian(ylim = c(0,1)) +
      labs(x = "Input concentration (ppb)", y = "Probability of acceptance (2.5th - 97.5th percentile)") +
      theme_bw() +
      theme(legend.position = "top")
    
  } else {
    stop("Unknown type.")
  }
}
```

1. Show the OC curve

```{r, echo = FALSE}
f_vis(data = result_cleaned, type = "OC", Mc = Mc)
```


2. Show the variance components VS input contamination level. 

```{r, echo = FALSE}
f_vis(data = result_cleaned, type = "var")
```

3. Show the true contamination level and contamination level from sampling VS input contamination level. This is a quality control step.

```{r, echo = FALSE}
f_vis(data = result_cleaned, type = "diag")
```

# Debug

```{r}
test1 = do.call(what = sim_outcome_val, args = c(ArgList_default, "seed" = NA))
test2 = sim_iterate_val(n_iter = 5, Args = ArgList_default, seed = 123)
test3 = sim_iterate2_val(n_seed = n_seed, n_iter = n_iter, Args = ArgList_default)
test4 = tune_param_val(Args = ArgList_default, n_seed = n_seed, n_iter = n_iter, param = "c_hat", val = c_hat)
```
